### 2020-10-25 misc/tex-macros/gohlatex-demo.tex
Some typos in gohlatex

\algstep A2. [Fall in love.] The formatting is so exquisite that you want to do things to it (write
your own \TeX\ macros).

@@

This is the end of a subsection

>>>>

\algstep A2. [Fall in love.] The formatting is so exquisite that you want to do unspeakable things to it (like
write your own \TeX\ macros).

@@

This is the end of a subsection.
